Network Configuration Synthesis with Abstract Topologies

### 2016-11-11 paper/abstraction/paper.tex
related work

\begin{easylist}[itemize]
& Topologies: DCell, BCube, Fattree, ...
& Topology Abstraction: Condor
& Memory Shape Analysis: Sagiv, others
& Configuration automation
& Configuration analysis
& Configuration synthesis
\end{easylist}

%Our work draws on four threads of prior work.%

%\para{Topology abstraction}%

%\para{Topology design}%

%\para{Configuration automation}
%Many practitioners use configuration templates~\cite{hatch,thwack}, to ensure certain kinds of consistency across similar devices. In addition, configuration languages such as RPSL~\cite{RFC2622}, Yang~\cite{RFC6020}, and Netconf~\cite{RFC6241} allow operators to express routing policy in a vendor-neutral way.
%However, all of these solutions remain low-level, for example, requiring operators to specify exact local preferences. Unlike \sysname, there is no guarantee that these low-level configurations satisfy the original, high-level intent.%

%\para{Configuration analysis}
%The notion that configuring network devices is difficult and error-prone is not new.
%In the past, researchers have tried to tackle this problem by analyzing existing
%router configurations~\cite{feamster+:rcc,ipassure,batfish,bagpipe,arc} and reporting errors or inconsistencies when they are detected.
%Our research is complementary to these analysis
%efforts.  We hope to eliminate bugs by using higher-level
%languages and a ``correct-by-construction''
%methodology. Writing configurations at a high level of abstraction simplifies policy implementation and prevents a whole host of low-level errors.%

>>>>

Our work is related to four threads of prior work.

\para{Network synthesis} Many recent systems focus on allowing operators to specify  their policies at a high level. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell the switches how to forward packets~\cite{x,y,z}. The second class, and to which our work belongs, targets conventional networks and generates switch configuration, based on which the switches interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}. Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

While we borrow much from existing configuration synthesis work, especially Propane~\cite{propane}, our goal is to generate role templates from abstract topologies, rather than switch configurations from concrete topologies. This goal aligns better with operators' mental models and tools and permits network evolution with minimal disruption to existing switches. In the process, develop new abstractions for network topologies, fault-tolerance analysis algorithms for abstract topologies, and assign formal semantics to templates.

\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{x,y,z}.  We do not develop new designs but develop abstractions that can capture these designs (and their evolution) and algorithms that can analyze the fault tolerance of abstract topologies.

While not the focus of this paper, our tools can enable operators to pick the right design for their networks, more quickly and with stronger guarantees. Today, when picking the design, operators analyze its multiple concrete instantiations because available analysis tools only work with concrete topologies~\cite{condor}. This process is time-consuming and not fool-proof; analyzing large, concrete topologies (with potentially thousands of nodes) takes a lot of time and the analysis does not cover the entire space of topologies that may arise.

\para{Network verification}
A complementary approach to reducing configuration errors is by analyzing the forwarding rules or configuration of the network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,symmetries}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must learn to express policies in a new language, but it saves them from the challenging and time-consuming task of configuration generation and provides stronger guarantees on correctness.

\para{Memory shape analysis} \todo{Sagiv, others}
